Automatic Identification and Annotation of Tasks in Structured Programs

### 2018-01-26 docs/ACM/paper.tex
added comments

%I don't know much of this part. I asked gleison to write me a paragraph and
%then I'll review it and try to write something here.

@@

%We need to discuss the THRESHOLD. Are we going to use
%César's experiments at Unicamp concerning the different runtimes? 
%Because if yes we need to think on how to write it.

@@

%I can work on that on the weekend!

@@

%I asked gleison and he'll sit with me to explain everything ,
%how it's done, and then I'll write it here.

>>>>

\pedro{I don't know much of this part. I asked gleison to write me a paragraph and
then I'll review it and try to write something here.}

@@

\pedro{We need to discuss the THRESHOLD. Are we going to use
César's experiments at Unicamp concerning the different runtimes? 
Because if yes we need to think on how to write it.}

@@

@@

\pedro{I asked gleison and he'll sit with me to explain everything ,
how it's done, and then I'll write it here.}
